Investigating Cross-Sectional Size Distribution of Randomly Distributed 3D Spheres

### 2020-05-24 Paper/main.tex
Moved figures into better positions

\usepackage[caption=false]{subfig}
\usepackage{todonotes}

@@

% The report headers
\markboth{PHYS6017 Computer Techniques in Physics Report 2, May 2020}
% do not delete next lines
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
  where $0.65 < R < 0.75$. The theoretical distribution is now different,
  although the experimental data still resembles this new distribution, showing
  a maximum around $R = 0.7$ and a sharp decrease after this. This is likely
  because there are more spheres with radii such that an overlap between $0$ and
  $0.7$ is possible, and relatively few spheres with radii such that a larger
  overlap is possible.}
\label{fig:random}
\end{center}
\end{figure}

@@

\begin{figure*}%[ht!]
  \centering
  \subfloat[Noise 2 orders of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
  \label{fig:2noise}}
  \centering
  \subfloat[Noise 1 order of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
  \label{fig:1noise}}
  \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
    each. Each recorded radius has a random noise added to it in order to
    determine how sensitive the data is to experimental
    error. Figure~\ref{fig:2noise} shows the distribution for an added noise 2
    orders of magnitude smaller than the recorded radius, while
    Figure~\ref{fig:1noise} is the same for noise 1 order of magnitude smaller. As
    we can see, the experimental data very resembles the theoretical
    distribution when noise of 2 orders of magnitude smaller are added. But this
    is not true when noise of 1 order of magnitude smaller is added, implying
    the data is very sensitive to experimental data.}
  \label{fig:noiseplots}
\end{figure*}

@@

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%
% \appendices{}
% \section{Appendix Name}
% Text

>>>>

\usepackage{blindtext, subfig}
\usepackage{dblfloatfix}

% \usepackage[caption=false]{subfig}
\usepackage{todonotes}

@@

% The report headers
\markboth{PHYS6017 Computer Techniques in Physics Report 2, May 2020}
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
  where $0.65 < R < 0.75$. The theoretical distribution is now different,
  although the experimental data still resembles this new distribution, showing
  a maximum around $R = 0.7$ and a sharp decrease after this. This is likely
  because there are more spheres with radii such that an overlap between $0$ and
  $0.7$ is possible, and relatively few spheres with radii such that a larger
  overlap is possible.}
\label{fig:random}
\end{center}
\end{figure}

\begin{figure*}[ht!]
  \centering
  \subfloat[Noise 2 orders of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
  \label{fig:2noise}}
  \centering
  \subfloat[Noise 1 order of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
  \label{fig:1noise}}
  \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
    each. Each recorded radius has a random noise added to it in order to
    determine how sensitive the data is to experimental
    error. Figure~\ref{fig:2noise} shows the distribution for an added noise 2
    orders of magnitude smaller than the recorded radius, while
    Figure~\ref{fig:1noise} is the same for noise 1 order of magnitude smaller. As
    we can see, the experimental data very resembles the theoretical
    distribution when noise of 2 orders of magnitude smaller are added. But this
    is not true when noise of 1 order of magnitude smaller is added, implying
    the data is very sensitive to experimental data.}
  \label{fig:noiseplots}
\end{figure*}

@@

@@

@@
